### 2016-04-22 manuscript-body.tex
Add sandwiches example from Kaczmarczyk et al

Clancy (2004) provides a comprehensive overview of this line of
research, though in the past decade it has only grown. Indeed, roughly
half the articles above were published in the ten years since Clancy's
overview.

@@

The first example comes from Kaczmarczyk et al. (2010). Part of that
study involved giving students snippets of Java code and asking students
to diagram (or pseudo-code) how the information would be stored in
memory. Below I have reproduced the code for Problem 2 (Kaczmarczyk et
al., 2010, p. 110):

Cheese{[}{]} cheeses = new Cheese{[}4{]};

Meat{[}{]} meats = new Meat{[}2{]};

Turkey turkey;

Ham ham;

RoastBeef roastBeef;

boolean lettuce = true;

boolean tomato = true;

SauceType sauceType = new SauceType();

int numMeat;

int numCheese;

@@

Student3 makes incorrect assumptions about connections between variables
to the extent that the student makes a mistake concerning the types of
the variables. As a result, the student places Objects of different
types in an array whose type matches none of them: ``And so because
there's two arrays, cheese and meats, uh, all those turkey and ham and
roast beef are gonna be sorted into the meats array.'' (Kaczmarczyk et
al., 2010, p. 110)

The researchers are correct in the sense that \textbf{turkey} and
\textbf{ham} and \textbf{roastBeef} will \emph{not} be sorted into the
\textbf{meats} array. First, there is no code here that places
\textbf{turkey} and \textbf{ham} in the array; there is only code that
declares them as variables. Moreover, as written, an attempt to place
\textbf{turkey} and \textbf{ham} and \textbf{roastBeef} into the array
would fail. Because of type restrictions in Java, only objects of class
Meat (or objects that inherit from class Meat) can go in the array.
\textbf{turkey} and \textbf{ham} and \textbf{roastBeef} are, perhaps
confusingly, references to object instances of classes \textbf{Turkey}
and \textbf{Ham} and \textbf{RoastBeef}, so in the current snippet they
cannot enter an array of type \textbf{Meat} because (1) they don't yet
exist as objects and (2) even if they did exist, their types don't match
the array's type. The authors call this misconception \emph{semantics to
semantics}, which occurs ``when the student inappropriately
assume{[}s{]} details about the relationship and operation of code
samples, although such information was neither given nor implied''
(Kaczmarczyk et al., 2010, p. 110).

>>>>

Clancy \cite{clancy_misconceptions_2004} provides a comprehensive overview of this line of
research, though in the past decade it has only grown. Indeed, roughly
half the articles above were published in the ten years since Clancy's
overview.

@@

The first example comes from \cite{kaczmarczyk_identifying_2010}. Part of that
study involved giving students snippets of Java code and asking students
to diagram (or pseudo-code) how the information would be stored in
memory. Below I have reproduced the code for Problem 2:

\hypertarget{sandiwches-code}{\label{sandwiches-code}}
\begin{Shaded}
\begin{Highlighting}[numbers=left,,]
\NormalTok{Cheese[] cheeses = }\KeywordTok{new} \NormalTok{Cheese[}\DecValTok{4}\NormalTok{];}
\NormalTok{Meat[] meats = }\KeywordTok{new} \NormalTok{Meat[}\DecValTok{2}\NormalTok{];}
\NormalTok{Turkey turkey;}
\NormalTok{Ham ham;}
\NormalTok{RoastBeef roastBeef;}
\DataTypeTok{boolean} \NormalTok{lettuce = }\KeywordTok{true}\NormalTok{;}
\DataTypeTok{boolean} \NormalTok{tomato = }\KeywordTok{true}\NormalTok{;}
\NormalTok{SauceType sauceType = }\KeywordTok{new} \FunctionTok{SauceType}\NormalTok{();}
\DataTypeTok{int} \NormalTok{numMeat;}
\DataTypeTok{int} \NormalTok{numCheese;}
\end{Highlighting}
\end{Shaded}

@@

\begin{quote}
  Student3 makes incorrect assumptions about connections between variables
  to the extent that the student makes a mistake concerning the types of
  the variables. As a result, the student places Objects of different
  types in an array whose type matches none of them: ``And so because
  there's two arrays, cheese and meats, uh, all those turkey and ham and
  roast beef are gonna be sorted into the meats array.'' \cite{kaczmarczyk_identifying_2010}
\end{quote}

The researchers are correct in the sense that \texttt{turkey} and
\texttt{ham} and \texttt{roastBeef} will \emph{not} be sorted into the
\texttt{meats} array. First, there is no code here that places
\texttt{turkey} and \texttt{ham} in the array; there is only code that
declares them as variables. Moreover, as written, an attempt to place
\texttt{turkey} and \texttt{ham} and \texttt{roastBeef} into the array
would fail. Because of type restrictions in Java, only objects of class
Meat (or objects that inherit from class Meat) can go in the array.
\texttt{turkey} and \texttt{ham} and \texttt{roastBeef} are, perhaps
confusingly, references to object instances of classes \texttt{Turkey}
and \texttt{Ham} and \texttt{RoastBeef}, so in the current snippet they
cannot enter an array of type \texttt{Meat} because (1) they don't yet
exist as objects and (2) even if they did exist, their types don't match
the array's type. The authors call this misconception \emph{semantics to
semantics}, which occurs ``when the student inappropriately
assume{[}s{]} details about the relationship and operation of code
samples, although such information was neither given nor implied''
\cite{kaczmarczyk_identifying_2010}.
